The MacLeish Package: R Package for analyzing weather and spatial data

### 2022-06-06 joss_paper/paper.Rmd
ran styler

```{r}
library(leaflet)
map <- leaflet() %>%
  addTiles() %>%
  addPolygons(
    data = macleish_layers[["boundary"]], 
    weight = 1, fillOpacity = 0.1
  ) %>%
  addPolygons(
    data = macleish_layers[["buildings"]], 
    weight = 1, popup = ~ name
  ) %>%
  addPolylines(
    data = macleish_layers[["trails"]], 
    weight = 1, color = "brown",
    popup = ~ name
  ) %>%
  addPolylines(
    data = macleish_layers[["streams"]], 
    weight = 2
  ) %>%
  addMarkers(
    data = filter(macleish_layers[["landmarks"]], grepl("Met", Label)), 
    popup = ~Label
  )
```

@@

```{r, warning=FALSE, echo=FALSE, fig.cap="Boxplot of tree diameter depending on species and position between 2010-2015."}
library(ggplot2)
tree_diameter1 %>%
  mutate(position = fct_relevel(position,
                                "emergent", "canopy", "subcanopy", 
                                "sapling")) %>%
  ggplot( aes(x=diameter, y=species, fill=position)) +
  geom_boxplot() +
  scale_fill_viridis_d(alpha=0.6, option="A") +
  scale_x_continuous(limits=c(0,60)) +
  facet_wrap(~year) +
  labs(x = "Diameter (cm)", y = "Species", fill = "Position", 
       title = "Distribution of Diameter Between 2010-2015") +
  theme(legend.position="bottom")
```

@@

```{r, warning=FALSE, echo=FALSE, fig.cap="Boxplot of tree diameter of Eastern Hemlock tree depending on position between 2010-2015."}
tree_diameter1 %>%
  mutate(position = fct_relevel(position,
                                "emergent", "canopy", "subcanopy", 
                                "sapling")) %>%
  ggplot(aes(x=diameter, y=species, fill=position)) +
  geom_boxplot() +
  scale_fill_viridis_d(alpha=0.6, option="A") +
  scale_y_discrete(limits=c("Eastern Hemlock")) +
  labs(x = "Diameter (cm)", y = "Species", fill = "Position", 
       title = "Distribution of Diameter for Eastern Hemlock") +
  theme(legend.position="bottom")
```

@@

```{r, warning=FALSE, echo=FALSE, fig.cap="Boxplot of tree diameter depending on species between 2009-2016."}
tree_diameter2 %>%
  ggplot( aes(x=diameter, y=species)) +
  geom_boxplot() +
  geom_jitter(color="black", size=0.4, alpha=0.9) +
  scale_fill_viridis_d(alpha=0.6, option="A") +
  scale_x_continuous(limits=c(0,60)) +
  facet_wrap(~year) +
  labs(x = "Diameter (cm)", y = "Species", 
       title = "Distribution of Diameter Between 2009-2016") +
  theme(legend.position="bottom")
```

>>>>

```{r}
library(leaflet)
map <- leaflet() %>%
  addTiles() %>%
  addPolygons(
    data = macleish_layers[["boundary"]],
    weight = 1, fillOpacity = 0.1
  ) %>%
  addPolygons(
    data = macleish_layers[["buildings"]],
    weight = 1, popup = ~name
  ) %>%
  addPolylines(
    data = macleish_layers[["trails"]],
    weight = 1, color = "brown",
    popup = ~name
  ) %>%
  addPolylines(
    data = macleish_layers[["streams"]],
    weight = 2
  ) %>%
  addMarkers(
    data = filter(macleish_layers[["landmarks"]], grepl("Met", Label)),
    popup = ~Label
  )
```

@@

```{r, warning=FALSE, echo=FALSE, fig.cap="Boxplot of tree diameter depending on species and position between 2010-2015."}
library(ggplot2)
tree_diameter1 %>%
  mutate(position = fct_relevel(
    position,
    "emergent", "canopy", "subcanopy",
    "sapling"
  )) %>%
  ggplot(aes(x = diameter, y = species, fill = position)) +
  geom_boxplot() +
  scale_fill_viridis_d(alpha = 0.6, option = "A") +
  scale_x_continuous(limits = c(0, 60)) +
  facet_wrap(~year) +
  labs(
    x = "Diameter (cm)", y = "Species", fill = "Position",
    title = "Distribution of Diameter Between 2010-2015"
  ) +
  theme(legend.position = "bottom")
```

@@

```{r, warning=FALSE, echo=FALSE, fig.cap="Boxplot of tree diameter of Eastern Hemlock tree depending on position between 2010-2015."}
tree_diameter1 %>%
  mutate(position = fct_relevel(
    position,
    "emergent", "canopy", "subcanopy",
    "sapling"
  )) %>%
  ggplot(aes(x = diameter, y = species, fill = position)) +
  geom_boxplot() +
  scale_fill_viridis_d(alpha = 0.6, option = "A") +
  scale_y_discrete(limits = c("Eastern Hemlock")) +
  labs(
    x = "Diameter (cm)", y = "Species", fill = "Position",
    title = "Distribution of Diameter for Eastern Hemlock"
  ) +
  theme(legend.position = "bottom")
```

@@

```{r, warning=FALSE, echo=FALSE, fig.cap="Boxplot of tree diameter depending on species between 2009-2016."}
tree_diameter2 %>%
  ggplot(aes(x = diameter, y = species)) +
  geom_boxplot() +
  geom_jitter(color = "black", size = 0.4, alpha = 0.9) +
  scale_fill_viridis_d(alpha = 0.6, option = "A") +
  scale_x_continuous(limits = c(0, 60)) +
  facet_wrap(~year) +
  labs(
    x = "Diameter (cm)", y = "Species",
    title = "Distribution of Diameter Between 2009-2016"
  ) +
  theme(legend.position = "bottom")
```
